---
title: "Correlation analysis"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Correlation analysis using large gene expression datasets
Analysis of correlations between mutational indicators (e.g., tumor mutational burden) and gene expression across large-scale datasets. This repository contains code, data processing workflows, and visualization tools for exploring these relationships.

# Structure the R project as follow:

```{r eval=FALSE}
├── README.md
├── data              <- Raw data, avoid editing directly.
├── data_interim      <- Intermidiate data that has be transformed.
├── data_processed    <- Final data sets for making plots and sharing.
├── scrips
|   ├── 1_process.r     <- Script to format raw data for correlation analysis (varies by input)
|   ├── 2_correlation.r <- Correlation script
|   ├── 3_plots.r       <- Script for plots and table outputs
├── results             <- Generated plots, tables, ppts
```

## Including Code
You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
